Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-25 writing/DraftExposurePaper/DraftExposurePaper.Rmd
note on ike data
add ike wind data

@@

>>>>

[JMF-- Missing values are those from Arkansas (missing the leading 0 in fips code)]

@@

```{r}
#Ike-2008 wind
#ike_wind <- read.csv("/Users/joshuaferreri/Documents/ike_wind.csv", na.strings = 999, header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_gauge.RData")
```
